Incentivizing Exploration with Unbiased History

### 2018-10-29 llevel-overview.tex
llevel intro update

\xhdr{Connecting structures between levels.} In our 3-level policy, the second level has $S = \Theta(\log(T))$ groups. We do so to ensure that in the small gap case, with high probability, both arms are pulled enough times in the second level. The argument relies on the fact that agents in different second-level groups observe disjoint histories of the first level and the independent randomness in first level groups guarantee each arm $a$ to have a ``lucky'' second-level group such that agents in that group all pull arm $a$ with high probability.

Simply generalizing this idea to an $L$-level policy would give us a $S$-ary tree like structure in the info graph. It incurs an extra $S^L$ factor in the expected regret. If we use $\log\log(T)$ levels as in Theorem \ref{thm:llevel-1}, this factor would be $\Omega\left(\log(T)^{\log\log(T)}\right)$ which is super poly-logarithmic. If we use $\log(T)/\log\log(T)$ levels as in Theorem \ref{thm:llevel-2}, this factor goes up to polynomial in $T$.

@@

For each level, we will have $S^2$ groups for some $S = \Theta(\log(T))$. The groups in the $l$-th level is labeled as $G_{l,u,v}$ for $u,v\in[S]$. For any $l \in \{2,...,L\}$ and $u,v,w\in [S]$, agents in group $G_{l,u,v}$ sees the history of agents in group $G_{l-1,v,w}$ (and by transitivity all agents in levels below $l-1$). See Figure \ref{fig:llevel-connecting} for a graphical view (as space limit, we only show 3 levels and 4 groups in each level). This connecting structure has three nice properties: \\
(i) The number of groups does not grow with the level and stays as $S^2 = \Theta(\log^2(T))$.  Having these groups only adds a $\Theta(\log^2(T))$ multiplicative factor to the expected regret.\\
(ii) Consider groups $G_{l-1,1,v},G_{l-1,2,v},...,G_{l-1,S,v}$ (e.g. $G_{l-1,1,1}$ and $G_{l-1,2,1}$ with red circles in the figure ) as a set of groups indexed by $l$ and $v$. The agents in a set of groups see the same history. They get ``lucky'' for some arm at the same time.\\
(iii) For each set of groups in level $l-1$, agents in the level $l$ see the history of agents in one of these groups. Therefore, we just need one set of groups in level $l-1$ to get ``lucky'' and then all agents in level $l$ will see enough pulls of arm $a$.

@@

 \draw [rounded corners=3mm, line width=1mm, red](-0.2,4.8)--(2.2,4.8)--(2.2,6.2)--(-0.2,6.2)--cycle;
  \draw [rounded corners=3mm, line width=1mm, red](5.8,4.8)--(8.2,4.8)--(8.2,6.2)--(5.8,6.2)--cycle;
\end{tikzpicture}
\caption{Connectiing structures between levels for the $L$-level policy.}
\label{fig:llevel-connecting}
\end{figure}
\xhdr{Additional groups for boundary cases.}

>>>>

\xhdr{Connecting structures between levels.} In our 3-level policy, the second level has $S = \Theta(\log(T))$ groups. We do so to ensure that in the small gap case (Lemma \ref{3levelsmallcase}), with high probability, both arms are pulled enough times in the second level. The argument relies on the fact that agents in different second-level groups observe disjoint histories of the first level and the independent randomness in first level groups guarantee each arm $a$ to have a ``lucky'' second-level group such that agents in that group all pull arm $a$ with high probability.

Simply generalizing this idea to an $L$-level policy would give us a $S$-ary tree like structure and the first level will have $S^{L-1}$ groups. It incurs an extra $S^{\Omega(L)}$ factor in the expected regret. If we use $\log\log(T)$ levels as in Theorem \ref{thm:llevel-1}, this factor super poly-logarithmic. If we use $\log(T)/\log\log(T)$ levels as in Theorem \ref{thm:llevel-2}, this factor goes up to polynomial in $T$.

@@

For each level, we will have $S^2$ groups for some $S = \Theta(\log(T))$. The groups in the $l$-th level is labeled as $G_{l,u,v}$ for $u,v\in[S]$. For any $l \in \{2,...,L\}$ and $u,v,w\in [S]$, agents in group $G_{l,u,v}$ sees the history of agents in group $G_{l-1,v,w}$ (and by transitivity all agents in levels below $l-1$). See Figure \ref{fig:llevel-connecting} for a graphical view (as space limit, we only show 3 levels and 4 groups in each level). This connecting structure has three nice properties: \\
(i) The number of groups does not grow with the level and stays as $S^2 = \Theta(\log^2(T))$.  Having these groups only adds a $\Theta(\log^2(T))$ multiplicative factor to the expected regret.\\
(ii) Consider groups $G_{l-1,1,v},G_{l-1,2,v},...,G_{l-1,S,v}$ (e.g. $G_{l-1,1,1}$ and $G_{l-1,2,1}$ with red circles in the figure ) as a set of groups indexed by $l-1$ and $v$. The agents in a set of groups see the same history. They get ``lucky'' for some arm at the same time.\\
(iii) For each set of groups in level $l-1$, agents in the level $l$ see the history of agents in one of these groups. Therefore, we just need one set of groups in level $l-1$ to get ``lucky'' and then all agents in level $l$ will see enough pulls of arm $a$.

@@

 \draw [rounded corners=3mm, line width=1mm, red](-0.2,4.8)--(2.2,4.8)--(2.2,6.2)--(-0.2,6.2)--cycle;
  \draw [rounded corners=3mm, line width=1mm, red](5.8,4.8)--(8.2,4.8)--(8.2,6.2)--(5.8,6.2)--cycle;
\end{tikzpicture}
\caption{Connectiing structures between levels for the $L$-level policy.}
\label{fig:llevel-connecting}
\end{figure}
\xhdr{Additional groups for boundary cases.} In our 3-level policy, recall the medium gap case (Lemma \ref{3levelmedium}) is the boundary case when the gap $|\mu_1-\mu_2|$ is $\Omega\left(\sqrt{\frac{1}{T_1}}\right)$ and $O\left(\sqrt{\frac{\log(T)}{T_1}}\right)$. In this case, the gap is not large enough to conclude that with high probability agents in both the second level and the third level all pull the best arm. The gap is also not small enough to conclude that with high probability both arms are explored enough times in the second level.

In our $L$-level policy, we resolve this problem by introducing an additional type of groups: $\Gamma$-groups and we call the original groups $G$-groups.
